\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Blake Buchman Problem Set 1}
\author{blakebuchman03 }
\date{January 2021}

\begin{document}

\maketitle

\section{Body}
I am interested in data science and economics because it ties directly into what I want to do as a career. I want to be a data analyst for a sports organization and to do that I must understand data science and economics. I have always been drawn to data because I think it is so important to everything in the world today. So many decisions are data driven and I believe in the business world you must make data driven decisions to stay caught up with everyone else. I took this class because I believe it will be able to teach me skills that I will actually use in the workplace. I want to be in classes that will give me lessons that I will actually use and I believe this one will do that for sure. I do not know what I want to do for the project in this class. My goals for this class are to learn those tools that I will use later on in life and to get an A to keep my GPA up. I believe that this class will be essential in my ability to really adapt when I get to an organization because the skills we will learn in this class are so essential at organization that I will be in if I want to be a data analyst.  My plan after graduation is to move to Fort Worth / Dallas, Texas and get a job as a data analyst or something similar. This area is full of potential jobs and there are a ton of sports organizations in the area, that is obviously my goal but there are a lot of other options if that does not turn out to be possible. I believe that will be a great place for me to start my career and it will make it to where I can find an organization to get started with and then try and climb the ladder from there either in that organization or in the industry as a whole.

\section{Equation}
\[ a^2 + b^2 = c^2 \]
\end{document}
